---
title: "R Notebook to study Eric's Analysis Code"
output: html_notebook
---
```{r}
#plyr can be used to manipulate data frames
library(plyr)
#ggplot is good for plotting
library(ggplot2)
#lmerTest loads mixed effects regressions and according t/z-tests
library(lmerTest)
#this is is cleaned data file
library(stringi)
library(stringr)
library(lsr)
dat<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/cleanedex2.csv')


```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

```{r}
#full data set without high RTs excluded
dl1<-dat
#excluding RTs
dl<-subset(dat, timecollect<=1000)
#what's the difference
1-nrow(dl)/nrow(dl1)
```

```{r}
#full data set without high RTs excluded
dl1<-subset(dat, trialinstruction %in% c('a', 'f'))
#excluding RTs
dl<-subset(dat, trialinstruction %in% c('a', 'f') & timecollect<=1000)
#what's the difference
1-nrow(dl)/nrow(dl1)
```


```{r}
#null model doesn't contain condition, but fixed and random intercept
mnull<-lmer(timecollect~1+(1|id), data=dl)
#alternative model contains condition is fixed effect
malternative<-lmer(timecollect~condition+(1|id), data=dl)
#is the alternative model significantly better than the null model
anova(mnull, malternative)#yes!
```

```{r}
summary(mnull)

```
```{r}
summary(malternative)
```

```{r}
#standard error function
se<-function(x){sd(x)/sqrt(length(x))}

#summarize data by condition
# sort according to the column of trial instruction, with different trial instructions
dp<-ddply(dl, ~trialinstruction, summarize, m=mean(timecollect), se=se(timecollect))
#dpp<-ddply(dl, ~instructioncollect, summarize, m=mean(timecollect), se = se(timecollect))
#recode trialinstruction
dp$trialinstruction<-ifelse(dp$trialinstruction=="a", "Accurate", "Fast")

#creat plot
p1 <- ggplot(dp, aes(y=m, x=trialinstruction, fill=trialinstruction)) +
  #show mean
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  #points
  geom_point()+
  #error bars +/- SEs
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #ylab
  ylab("RT")+
  #x-lab
  xlab("Condition")+ 
  #theme
  theme_classic()+
  #fills
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme change
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color=FALSE, shape=FALSE)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,550)) +
  
  #title
  ggtitle("Average RTs") + 
            theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+  
  coord_fixed(0.004)
#show
p1
```

```{r}
#null model doesn't contain condition, but fixed and random intercept
#logistic regression via family=binomial
mnull<-glmer(correctcollect~1+(1|id), data=dl, family='binomial')
#estimate alternative model
malternative<-glmer(correctcollect~condition+(1|id), data=dl, family='binomial')
#is the alternative model significantly better than the null model
anova(mnull, malternative)#yes!
```

```{r}
#is the effect significant and in the right direction
summary(malternative)#yes!
```



```{r}
#summarize data by condition
dp<-ddply(dl, ~trialinstruction, summarize, m=mean(correctcollect), se=se(correctcollect))
#recode trialinstruction
dp$trialinstruction<-ifelse(dp$trialinstruction=="a", "Accurate", "Fast")

#creat plot
p2 <- ggplot(dp, aes(y=m, x=trialinstruction, fill=trialinstruction)) +
  #show mean
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  #points
  geom_point()+
  #error bars +/- SEs
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #ylab
  ylab("P(correct)")+
  #x-lab
  xlab("Condition")+ 
  #theme
  theme_classic()+
  #fills
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme change
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color=FALSE, shape=FALSE)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,1)) +
  #title
  ggtitle("Average Correct Responses")+
              theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+  
  
  coord_fixed(2.2)
#show
p2
```

```{r}
library(stringi)
library(stringr)
library(lsr)

#remove braces
dat$keyassignment<-str_replace(dat$keyassignment, '\\[', '')
dat$keyassignment<-str_replace(dat$keyassignment, '\\]', '')

#current instruction
dat$current<-dat$instructioncollect

#last instruction
dat$last<-c(1, paste(dat$instructioncollect[-nrow(dat)]))# I don't understand what is meant by -nrow(dat)??

#only look at neutral blocks
dd<-subset(dat, trialinstruction=="n")
#remove first trial per block, since that doesn't have previous instruction
dd<-subset(dd, trialcollect!=1)
dd$condition<-ifelse(dd$condition==0, "fast", dd$condition)
dd$condition<-ifelse(dd$condition==1, "accurate", dd$condition)

#get A, B, C, and D
a<-substr(dd$keyassignment, 2, 2)
b<-substr(dd$keyassignment, 7, 7)
c<-substr(dd$keyassignment, 12, 12)
d<-substr(dd$keyassignment, 17, 17)

#label first and last two blocks
dd$block<-rep(rep(c("first", "last"), each=198), length(unique(dat$id)))

#creat signed Cohen's d
mycohen<-function(x, y){
  #needs to be longer than 3
  if (length(x)>4 & length(y>4)){
  #Cohen's d  
  d<-cohensD(x, y)
  #sign based on mean
  if (mean(x)<mean(y)){d<- -d}
  }else { d<-NA}#NA if smaller than 3
  #return d
  return(d)
}

#mark all chunks and their controls
dd$chunkab<-ifelse((dd$last==a & dd$current==b), 1, 0)
dd$controlab<-ifelse((dd$last==a & dd$current!=b), 1, 0)
dd$chunkcd<-ifelse((dd$last==c & dd$current==d), 1, 0)
dd$controlcd<-ifelse((dd$last==c & dd$current!=d), 1, 0)
dd$chunkbc<-ifelse((dd$last==b & dd$current==c), 1, 0)
dd$controlbc<-ifelse((dd$last==b & dd$current!=c), 1, 0)
dd$chunkda<-ifelse((dd$last==d & dd$current==a), 1, 0)
dd$controlda<-ifelse((dd$last==d & dd$current!=a), 1, 0)

#we select RTs smaller than 1000ms
tselect<-1000

#get all Cohen's ds
dchunkab<-ddply(subset(dd, chunkab==1 & timecollect<=tselect), ~id, summarize,
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d# get the dth column from the 

dchunkabcontrol<-ddply(subset(dd, controlab==1 & timecollect<=tselect), ~id, summarize, 
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkcd<-ddply(subset(dd, chunkcd==1 & timecollect<=tselect), ~id, summarize, 
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkcdcontrol<-ddply(subset(dd, controlcd==1 & timecollect<=tselect), ~id, summarize, 
                       d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkbc<-ddply(subset(dd, chunkbc==1 & timecollect<=tselect), ~id, summarize, 
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkbccontrol<-ddply(subset(dd, controlbc==1 & timecollect<=tselect), ~id, summarize, 
                       d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkda<-ddply(subset(dd, chunkda==1 & timecollect<=tselect), ~id, summarize, 
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d

dchunkdacontrol<-ddply(subset(dd, controlda==1 & timecollect<=tselect), ~id, summarize, 
                d=mycohen(timecollect[block=="first"], timecollect[block=="last"]))$d


#labe condition
# ddply(dat, ~id, summarize, cond=trialinstruction[201]) sort based on condition
cond<-ifelse(ddply(dat, ~id, summarize, cond=trialinstruction[201])$cond=="f", "Fast", "Accurate")
#for true delta, we need to subtract control
data_delta<-data.frame(dchange=c(dchunkab-dchunkabcontrol, dchunkbc-dchunkbccontrol, dchunkcd-dchunkcdcontrol, dchunkda-dchunkdacontrol),
               cond=rep(cond, 4), id=rep(ddply(dat, ~id, summarize, cond=trialinstruction[201])$id, 4),
               trans=rep(c('high', 'med', 'high', 'med'), length(dchunkdacontrol)))


#fit without condition
m1<-lmer(dchange~1+(1|id), data=data_delta)
#with condition
m2<-lmer(dchange~cond+(1|id), data=data_delta)
#which one is better?
anova(m1,m2)
```

```{r}
summary(m2)
```

```{r}
#summarize data for plotting
dp<-ddply(na.omit(data_delta), ~cond, summarize, m=mean(dchange), se=se(dchange))

#create plot
p3 <- ggplot(dp, aes(y=m, x=cond, fill=cond)) +
  #mean 
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  #points
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"d"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme 
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color=FALSE, shape=FALSE)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,0.45)) +
  #title
  ggtitle("Chunky boost") +
                theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+  
  coord_fixed(4.5)
#show!
p3

```
```{r}
ddabrt<-subset(dd, chunkab==1 & timecollect<=tselect)
ddabrtsum <- data_summary(ddabrt, varname="timecollect", groupnames=c("condition", "block"))
ddabrtsum$ck <- rep("ab",times=4)
ddnabrt<-subset(dd, controlab==1 & timecollect<=tselect)
ddnabrtsum <- data_summary(ddnabrt, varname="timecollect", groupnames=c("condition", "block"))
ddnabrtsum$ck <- rep("nab",times=4)

ddabckrtsum<-rbind(ddabrtsum,ddnabrtsum)
library(ggplot2)
#library(hrbrthemes)
 
# Graph
ggplot(ddabckrtsum, aes(fill=block, y=timecollect, x=condition)) + 
    geom_bar(position="dodge", color="black", stat="identity") +
    geom_errorbar(aes(ymin=timecollect-sd, ymax=timecollect+sd), width=.2,
                 position=position_dodge(.9)) +
    ggtitle("ab and control") +
    facet_wrap(~ck) +
     theme_classic() +
   scale_fill_manual(labels = c("Baseline", "Test"),values=c('#999999','#E69F00'))+
    xlab("Condition") + ylab("Reaction Time")
```
```{r}
ddbcrt<-subset(dd, chunkbc==1 & timecollect<=tselect)
ddbcrtsum <- data_summary(ddbcrt, varname="timecollect", groupnames=c("condition", "block"))
ddbcrtsum$ck <- rep("bc",times=4)
ddnbcrt<-subset(dd, controlbc==1 & timecollect<=tselect)
ddnbcrtsum <- data_summary(ddnbcrt, varname="timecollect", groupnames=c("condition", "block"))
ddnbcrtsum$ck <- rep("nbc",times=4)
ddbcckrtsum<-rbind(ddbcrtsum,ddnbcrtsum) # combine the two dataframe into one


# Graph
ggplot(ddbcckrtsum, aes(fill=block, y=timecollect, x=condition)) + 
    geom_bar(position="dodge", color="black", stat="identity") +
    geom_errorbar(aes(ymin=timecollect-sd, ymax=timecollect+sd), width=.2,
                 position=position_dodge(.9)) +
    ggtitle("bc and control") +
    facet_wrap(~ck) +
     theme_classic() +
   scale_fill_manual(labels = c("Baseline", "Test"),values=c('#999999','#E69F00'))+
    xlab("Condition") + ylab("Reaction Time")
```
```{r}
ddcdrt<-subset(dd, chunkcd==1 & timecollect<=tselect)
ddcdrtsum <- data_summary(ddcdrt, varname="timecollect", groupnames=c("condition", "block"))
ddcdrtsum$ck <- rep("cd",times=4)
ddncdrt<-subset(dd, controlcd==1 & timecollect<=tselect)
ddncdrtsum <- data_summary(ddncdrt, varname="timecollect", groupnames=c("condition", "block"))
ddncdrtsum$ck <- rep("ncd",times=4)
ddcdckrtsum<-rbind(ddcdrtsum,ddncdrtsum) # combine the two dataframe into one


# Graph
ggplot(ddcdckrtsum, aes(fill=block, y=timecollect, x=condition)) + 
    geom_bar(position="dodge", color="black", stat="identity") +
    geom_errorbar(aes(ymin=timecollect-sd, ymax=timecollect+sd), width=.2,
                 position=position_dodge(.9)) +
    ggtitle("cd and control") +
    facet_wrap(~ck) +
     theme_classic() +
   scale_fill_manual(labels = c("Baseline", "Test"),values=c('#999999','#E69F00'))+
    xlab("Condition") + ylab("Reaction Time")
```
```{r}
dddart<-subset(dd, chunkda==1 & timecollect<=tselect)
dddartsum <- data_summary(dddart, varname="timecollect", groupnames=c("condition", "block"))
dddartsum$ck <- rep("da",times=4)
ddndart<-subset(dd, controlda==1 & timecollect<=tselect)
ddndartsum <- data_summary(ddndart, varname="timecollect", groupnames=c("condition", "block"))
ddndartsum$ck <- rep("nda",times=4)
dddackrtsum<-rbind(dddartsum,ddndartsum) # combine the two dataframe into one


# Graph
ggplot(dddackrtsum, aes(fill=block, y=timecollect, x=condition)) + 
    geom_bar(position="dodge", color="black", stat="identity") +
    geom_errorbar(aes(ymin=timecollect-sd, ymax=timecollect+sd), width=.2,
                 position=position_dodge(.9)) +
    ggtitle("da and control") +
    facet_wrap(~ck) +
     theme_classic() +
   scale_fill_manual(labels = c("Baseline", "Test"),values=c('#999999','#E69F00'))+
    xlab("Condition") + ylab("Reaction Time")
```

```{r}
#select neutral blocks
dd<-subset(dat, trialinstruction=="n")
#extract A,B,C,D
dd$a<-substr(dd$keyassignment, 2, 2)
dd$b<-substr(dd$keyassignment, 7, 7)
dd$c<-substr(dd$keyassignment, 12, 12)
dd$d<-substr(dd$keyassignment, 17, 17)
#blocks
dd$block<-rep(rep(c("first", "last"), each=200), length(unique(dat$id)))
#collection frames
dc1<-dc2<-dc3<-dc4<-dc5<-data.frame(id=numeric(), cond=numeric(), rt1=numeric(), rt2=numeric(), block=numeric())
#loop through
for (i in 1:length(unique(dd$id))){
  ddk<-subset(dd, id==unique(dd$id)[i])
  #loop through first and last
  for (nb in c("first", "last")){
    #select
    ddn<-subset(ddk, block==nb)
    #get a,b,c
    a<-ddn$a[1]
    b<-ddn$b[1]
    c<-ddn$c[1]
    d<-ddn$d[1]
    for (n in 3:nrow(ddn)){
      #get all chunks of size 3
      if (paste(ddn$instructioncollect[n-2])==a & paste(ddn$instructioncollect[n-1])==b & paste(ddn$instructioncollect[n])==c){
        dc1<-rbind(dc1, data.frame(id=ddn$id[n], cond=ifelse(ddn$condition[n]==0, "fast", "accurate"), rt1=ddn$timecollect[n-1], rt2=ddn$timecollect[n], block=ddn$block[n]))
      }
      if (paste(ddn$instructioncollect[n-2])==c & paste(ddn$instructioncollect[n-1])==d & paste(ddn$instructioncollect[n])==a){
        dc2<-rbind(dc2, data.frame(id=ddn$id[n], cond=ifelse(ddn$condition[n]==0, "fast", "accurate"), rt1=ddn$timecollect[n-1], rt2=ddn$timecollect[n], block=ddn$block[n]))
      }
      if (paste(ddn$instructioncollect[n-2])==b & paste(ddn$instructioncollect[n-1])==c & paste(ddn$instructioncollect[n])==d){
        dc3<-rbind(dc3, data.frame(id=ddn$id[n], cond=ifelse(ddn$condition[n]==0, "fast", "accurate"), rt1=ddn$timecollect[n-1], rt2=ddn$timecollect[n], block=ddn$block[n]))
      }
      if (paste(ddn$instructioncollect[n-2])==d & paste(ddn$instructioncollect[n-1])==a & paste(ddn$instructioncollect[n])==b){
        dc4<-rbind(dc4, data.frame(id=ddn$id[n], cond=ifelse(ddn$condition[n]==0, "fast", "accurate"), rt1=ddn$timecollect[n-1], rt2=ddn$timecollect[n], block=ddn$block[n]))
      }#get everything that isn't a chunk of size 3
      if (!(paste(ddn$instructioncollect[n-2])==a & paste(ddn$instructioncollect[n-1])==b & paste(ddn$instructioncollect[n])==c) &
          !(paste(ddn$instructioncollect[n-2])==c & paste(ddn$instructioncollect[n-1])==d & paste(ddn$instructioncollect[n])==a) &
          !(paste(ddn$instructioncollect[n-2])==b & paste(ddn$instructioncollect[n-1])==c & paste(ddn$instructioncollect[n])==d) &
          !(paste(ddn$instructioncollect[n-2])==d & paste(ddn$instructioncollect[n-1])==a & paste(ddn$instructioncollect[n])==b)){
        dc5<-rbind(dc5, data.frame(id=ddn$id[n], cond=ifelse(ddn$condition[n]==0, "fast", "accurate"), rt1=ddn$timecollect[n-1], rt2=ddn$timecollect[n], block=ddn$block[n]))
      }
    }
  }
}

#library for Wasserstein
library(transport)
wasserst<-function(x,y){
  #at least 5 long
  if (length(x)>=5){dist<-wasserstein1d(x, y)}
  else {dist<-NA}#otherwise NA
  return(dist)
}

#get the Wasserstein distances, again removing RTs<1000ms
m1<-ddply(subset(dc1,rt1 <=1000 & rt2<=1000), ~id+cond, summarize, diff=wasserst(rt1[block=="first"], rt2[block=="first"])-wasserst(rt1[block=="last"], rt2[block=="last"]))
m2<-ddply(subset(dc2,rt1 <=1000 & rt2<=1000), ~id+cond, summarize, diff=wasserst(rt1[block=="first"], rt2[block=="first"])-wasserst(rt1[block=="last"], rt2[block=="last"]))
m3<-ddply(subset(dc3,rt1 <=1000 & rt2<=1000), ~id+cond, summarize, diff=wasserst(rt1[block=="first"], rt2[block=="first"])-wasserst(rt1[block=="last"], rt2[block=="last"]))
m4<-ddply(subset(dc4,rt1 <=1000 & rt2<=1000), ~id+cond, summarize, diff=wasserst(rt1[block=="first"], rt2[block=="first"])-wasserst(rt1[block=="last"], rt2[block=="last"]))
m5<-ddply(subset(dc5,rt1 <=1000 & rt2<=1000), ~id+cond, summarize, diff=wasserst(rt1[block=="first"], rt2[block=="first"])-wasserst(rt1[block=="last"], rt2[block=="last"]))


#bind them
m<-rbind(m1, m2, m3, m4)
#get the change per condition and id
dp<-ddply(m, ~cond+id, summarize, m=mean(diff, na.rm=TRUE))
#control for no chunks
dp$m<-dp$m-m5$diff

#no effect
m1<-lmer(diff~1+(1|id), data=na.omit(m))
#effect of condition
m2<-lmer(diff~cond+(1|id), data=na.omit(m))
#which one is better?
anova(m1, m2)
```


```{r}
summary(m2)
```

```{r}
#pextract means
dm<-ddply(dp, ~cond, summarize, m=mean(m), se=se(as.numeric(m)))
dm$se[1]<-se(subset(dp, cond=='accurate')$m)
dm$se[2]<-se(subset(dp, cond=='fast')$m)
#condtiions
dm$cond<-ifelse(dm$cond=="fast", "Fast", "Accurate")

#plot
p4 <- ggplot(dm, aes(y=m, x=cond, fill=cond)) +
  #mean
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  #points
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #ylab
  ylab(expression(Delta~"Wasserstein"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+
  #scale fill
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme change
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color=FALSE, shape=FALSE)+
  #line at 0
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(-2.8,20)) +
  #title
  ggtitle("Chunkiness") +
          theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
  coord_fixed(0.1)
#show
p4
```

```{r}
#ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2dckfq.csv')
ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2cleaneddckfq.csv')
ckfq$condition<-ifelse(ckfq$condition=="fast", "Fast", ckfq$condition)
ckfq$condition<-ifelse(ckfq$condition==1, "Accurate", ckfq$condition)

ckfqhigh2<-subset(ckfq, chunk=="high2")

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckfqhigh2), ~condition, summarize, m=mean(delta_c),
          se=se(delta_c))

dp$condition<-ifelse(dp$condition==1, "Accurate", dp$condition)


dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p6 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"N"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,25)) +
            theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
  
  ggtitle("High Transition") +
  coord_fixed(0.1)

#show!
p6
```
```{r}
ckfqhigh2$condition <- factor(ckfqhigh2$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))
#fit without condition
m1<-lm(delta_c~1, data=ckfqhigh2)
m2<-lm(delta_c~condition, data=na.omit(ckfqhigh2))
anova(m1,m2)
```

```{r}
ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2cleaneddckfq.csv')
ckfq$condition<-ifelse(ckfq$condition=="fast", "Fast", ckfq$condition)
ckfq$condition<-ifelse(ckfq$condition==1, "Accurate", ckfq$condition)

ckfqmed2<-subset(ckfq, chunk=="medium2")

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckfqmed2), ~condition, summarize, m=mean(delta_c),
          se=se(delta_c))
dp$condition<-ifelse(dp$condition==1, "Accurate", dp$condition)


dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p7 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"N"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,25)) +
  ggtitle("Medium Transition") + 
              theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
  coord_fixed(0.1)

#show!
p7
```
```{r}
ckfqmed2$condition <- factor(ckfqmed2$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))
#fit without condition
m1<-lm(delta_c~1, data=ckfqmed2)
m2<-lm(delta_c~condition, data=na.omit(ckfqmed2))
anova(m1,m2)
```

```{r}
ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2cleaneddckfq.csv')
ckfq$condition<-ifelse(ckfq$condition=="fast", "Fast", "Accurate")
#ckfq$condition<-ifelse(ckfq$condition=="accurate", "Accurate", ckfq$condition)

ckfqsz3<-subset(ckfq, chunk=="sz3")

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckfqsz3), ~condition, summarize, m=mean(delta_c),
          se=se(delta_c))
dp$condition<-ifelse(dp$condition==1, "Accurate", dp$condition)


dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p8 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"N"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,40)) +
  ggtitle("Size 3 Chunks") +
                theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
  
  coord_fixed(0.08)
#show!
p8
```

```{r}
ckfqsz3$condition <- factor(ckfqsz3$condition)
#fit without condition
m1<-lm(delta_c~1, data=ckfqsz3)
m2<-lm(delta_c~condition, data=na.omit(ckfqsz3))
anova(m1,m2)
```
```{r}
ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2cleaneddckfq.csv')
ckfq$condition<-ifelse(ckfq$condition=="fast", "Fast", ckfq$condition)
ckfq$condition<-ifelse(ckfq$condition=="accurate", "Accurate", ckfq$condition)

ckfqsz4<-subset(ckfq, chunk=="sz4")

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckfqsz4), ~condition, summarize, m=mean(delta_c),
          se=se(delta_c))
dp$condition<-ifelse(dp$condition==1, "Accurate", dp$condition)


dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p9 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"N"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,28)) +
                  theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
    coord_fixed(0.08)+

  ggtitle("Size 4 Chunks")
#show!
p9
```

```{r}
ckfq<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/exp2cleaneddckfq.csv')
ckfq$condition<-ifelse(ckfq$condition=="fast", "Fast", "Accurate")
#ckfq$condition<-ifelse(ckfq$condition=="accurate", "Accurate", ckfq$condition)

ckfqsz3<-subset(ckfq, chunk != 'sz4')

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckfqsz3), ~condition, summarize, m=mean(delta_c),
          se=se(delta_c))
dp$condition<-ifelse(dp$condition==1, "Accurate", dp$condition)


dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p8 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab(expression(Delta~"N"))+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,28)) +
  ggtitle("Chunk Increase") +
                theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+ 
  
  coord_fixed(0.08)
#show!
p8
```

```{r}
ckfq$condition <- factor(ckfq$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))
#fit without condition
m1<-lm(delta_c~1, data=ckfq)
m2<-lm(delta_c~condition, data=na.omit(ckfq))
anova(m1,m2)
```


```{r}
ckru<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/chunkreusep.csv')
ckru<-subset(ckru, condition %in% c('Accurate', 'Fast'))

#for true delta, we need to subtract control

se<-function(x){sd(x)/sqrt(length(x))}

dp<-ddply(na.omit(ckru), ~condition, summarize, m=mean(reuse_p),
          se=se(reuse_p))

dp$condition <- factor(dp$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))

#create plot
p10 <- ggplot(dp, aes(y=m, x=condition, fill=condition)) +
  #mean 
  stat_summary(fun = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #text, expression changes the Delta to a Greek letter
  ylab("P")+
  #xlab
  xlab("Condition")+ 
  #theme
  theme_classic()+#
  #color scheme
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  #theme
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color="none", shape="none")+
  #scale y
  geom_hline(yintercept=0)+
  #scale y
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,1)) +
  ggtitle("Chunk Reuse Probability") +
                    theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+
  coord_fixed(2)

#show!
p10
```

```{r}
ckru$condition <- factor(ckru$condition,                                    # Change ordering manually
                  levels = c("Accurate", "Fast"))
#fit without condition
m1<-lm(reuse_p~1, data=ckru)
m2<-lm(reuse_p~condition, data=na.omit(ckru))
anova(m1,m2)
```



```{r}
library(stringi)
library(stringr)
library(lsr)
#via trial and error, I saw in which position they are in in this string, we assume A-B-C-D-A has transitions High-Medium-High-Medium
dat<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/cleanedex2.csv')

dat$keyassignment<-str_replace(dat$keyassignment, '\\[', '')
dat$keyassignment<-str_replace(dat$keyassignment, '\\]', '')

dd<-subset(dat, trialinstruction=="n")

dd$block<-rep(rep(c("first", "last"), each=200), length(unique(dd$id)))

dd<-subset(dd, block=="last")

#current instruction
dd$current<-dd$instructioncollect

#last instruction
dd$last<-c(1, paste(dd$instructioncollect[-nrow(dd)]))

a<-substr(dd$keyassignment, 2, 2)
b<-substr(dd$keyassignment, 7, 7)
c<-substr(dd$keyassignment, 12, 12)
d<-substr(dd$keyassignment, 17, 17)

dd$truth<-ifelse(paste(dd$last)==a & paste(dd$current)==b, 0.9, 0)
dd$truth<-ifelse(paste(dd$last)==b & paste(dd$current)==c, 0.7, dd$truth)
dd$truth<-ifelse(paste(dd$last)==c & paste(dd$current)==d, 0.9, dd$truth)
dd$truth<-ifelse(paste(dd$last)==d & paste(dd$current)==a, 0.7, dd$truth)
dd$truth<-ifelse(paste(dd$last)==a & paste(dd$current)==a| paste(dd$last)==a & paste(dd$current)==c|paste(dd$last)==a & paste(dd$current)==d,0.1/3 , dd$truth)
dd$truth<-ifelse(paste(dd$last)==b & paste(dd$current)==a| paste(dd$last)==b & paste(dd$current)==b|paste(dd$last)==b & paste(dd$current)==d,0.1 , dd$truth)
dd$truth<-ifelse(paste(dd$last)==c & paste(dd$current)==a| paste(dd$last)==c & paste(dd$current)==b|paste(dd$last)==c & paste(dd$current)==c,0.1/3 , dd$truth)
dd$truth<-ifelse(paste(dd$last)==d & paste(dd$current)==d| paste(dd$last)==a & paste(dd$current)==c|paste(dd$last)==a & paste(dd$current)==d,0.1 , dd$truth)

#exaggerated transitions
dd$chunky<-ifelse(paste(dd$last)==a & paste(dd$current)==b, 1, 0)
dd$chunky<-ifelse(paste(dd$last)==b & paste(dd$current)==c, 1, dd$chunky)
dd$chunky<-ifelse(paste(dd$last)==c & paste(dd$current)==d, 1, dd$chunky)
dd$chunky<-ifelse(paste(dd$last)==d & paste(dd$current)==a, 1, dd$chunky)

#z-transform
dd$chunky<-as.numeric(scale(dd$chunky))
dd$truth<-as.numeric(scale(dd$truth))
#full model
m1<-lmer(log(timecollect)~condition*chunky+condition*truth+(1|id), data=subset(dd, timecollect<=1000 & correctcollect==1))
#lesioned model
m2<-lmer(log(timecollect)~chunky+truth+(1|id), data=subset(dd, timecollect<=1000 & correctcollect==1))
#which one better?
anova(m1,m2)#m1
```

```{r}
summary(m1)
```

```{r}
#extract summaries
sm1<-summary(m1)
#extract coefficients
m<-c(sm1$coefficients[5,1], sm1$coefficients[6,1]) 
se<-c(sm1$coefficients[5,2], sm1$coefficients[6,2])

#data frame
dp<-data.frame(m, se, effect=c('Chunky', 'True'))
#effect
dp$effect<-factor(dp$effect, levels=c('True', 'Chunky'))

#data frame
#dp<-data.frame(m, se, effect=c('Chunky', 'Truth'))
#effect
#dp$effect<-factor(dp$effect, levels=c('Truth', 'Chunky'))
#show plot
p6 <- ggplot(dp, aes(y=m, x=effect, fill=effect)) +
  #show mean
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.5) + 
  #point
  geom_point()+
  #error bar
  geom_errorbar(aes(ymin=m-se, ymax=m+se),color='black', width = .25, position=position_dodge((width=0.9))) +
  #labs
  ylab(expression(beta))+
  xlab("Effect")+ 
  #classic theme
  theme_classic()+
  #fills
  scale_fill_manual(values=(c("#808080",  "#808080")))+
  #theme change
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  #no legend
  guides(color=FALSE, shape=FALSE)+
  #line at 0
  geom_hline(yintercept=0)+
  #scale y
  #scale_y_continuous(expand = c(0,0),
  #                   limits = c(-0.042,0.04)) +
  #title
                      theme(text = element_text(size=24),
            legend.text = element_text(size = 20))+
  ggtitle("Chunky RTs")
#show!
p6
```
fast is coded as a 1, and accyrate as a 0, 

condition fast has a positive interaction effect with truth to the reaction time. 
condition fast as a negative interaction effect with chunky to the reaction time. 

as the condition goes from accurate to fast, reaction time increases more with the true transition. 

As the condition goes from accurate to fast, reaction time descreases more with the chunky transitions. 

Compared to the chunky transition, the truth condition have a more positive interaction with the fast conditgion on influencing the reaction time.
The chunky transition, compared to the truth condition, have a negative interaction with the fast condition on influencing the reaction time, 

```{r}
#we only look at the neutral blocks, i.e. the first two and the last two
dat<-read.csv('/kyb/rg/swu/Nextcloud/Documents/chunking/data/data_plos_exp12/cleanedex2.csv')

dd<-subset(dat, trialinstruction=="n")

dd$block<-rep(rep(c("first", "last"), each=200), length(unique(dd$id)))

dd<-subset(dd, block=="last")

#via trial and error, I saw in which position they are in in this string, we assume A-B-C-D-A has transitions High-Medium-High-Medium
a<-substr(dd$keyassignment, 2, 2)
b<-substr(dd$keyassignment, 7, 7)
c<-substr(dd$keyassignment, 12, 12)
d<-substr(dd$keyassignment, 17, 17)

dd$truth<-ifelse(paste(dd$last)==a & paste(dd$current)==b, 0.8, 0)
dd$truth<-ifelse(paste(dd$last)==b & paste(dd$current)==c, 0.4, dd$truth)
dd$truth<-ifelse(paste(dd$last)==c & paste(dd$current)==d, 0.8, dd$truth)
dd$truth<-ifelse(paste(dd$last)==d & paste(dd$current)==a, 0.4, dd$truth)

dd$chunky<-ifelse(paste(dd$last)==a & paste(dd$current)==b, 1, 0)
dd$chunky<-ifelse(paste(dd$last)==b & paste(dd$current)==c, 1, dd$chunky)
dd$chunky<-ifelse(paste(dd$last)==c & paste(dd$current)==d, 1, dd$chunky)
dd$chunky<-ifelse(paste(dd$last)==d & paste(dd$current)==a, 1, dd$chunky)


dd$id<-as.factor(dd$id)
dd$condition<-ifelse(dd$condition==1, "accurate", "fast")
dd$chunky<-as.numeric(scale(dd$chunky))
dd$truth<-as.numeric(scale(dd$truth))
head(dd)
```
```{r}
dd$chunkresp<-ifelse(paste(dd$last)==a & paste(dd$userpress)==b, 1, 0)
dd$chunkresp<-ifelse(paste(dd$last)==b & paste(dd$userpress)==c, 1, dd$chunkresp)
dd$chunkresp<-ifelse(paste(dd$last)==c & paste(dd$userpress)==d, 1, dd$chunkresp)
dd$chunkresp<-ifelse(paste(dd$last)==d & paste(dd$userpress)==a, 1, dd$chunkresp)
dd$incorrect<-ifelse(dd$correctcollect==1, 0, 1)

m1<-glmer(chunkresp~condition*correctcollect+(1|id), data=dd, family="binomial")
```

```{r}
m2<-glmer(chunkresp~correctcollect+(1|id), data=dd, family="binomial")
anova(m1,m2)
```

```{r}
sm1<-summary(m1)
m<-c(sm1$coefficients[2,1], sm1$coefficients[4,1]) 
se<-c(sm1$coefficients[2,2], sm1$coefficients[4,2])
dp<-data.frame(m, se, effect=c('Fast', 'Accurate'))
p5 <- ggplot(dp, aes(y=m, x=effect, fill=effect)) +
  scale_fill_manual(values=(c("#5F4B8BFF", "#E69A8DFF")))+
  theme(text = element_text(size=21,  family="sans"), strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  guides(color=FALSE, shape=FALSE)+
  geom_hline(yintercept=0)+
  scale_y_continuous(expand = c(0,0),
                     limits = c(-0.52,0.6)) +
  ggtitle("e: Chunky responses")
p5
```

